### 2018-05-16 manuscript.tex
all ms recompiled

\section*{Availability and Future Directions}
All packages in the \texttt{rethomics} framework are available under the terms of the GPLv3 license and listed at
\href{https://github.com/rethomics}{https://github.com/rethomics/}.
Extensive installation instructions, as well as reproducible demos and tutorials, are available at
\href{https://rethomics.github.io/}{https://rethomics.github.io/}.
All packages are continuously integrated and unit tested on several versions of \texttt{R} to minimise the risk of present and future issues.

Several users, in different research groups, have already adopted and are contributing to the future development framework.
Several new packages in the \texttt{rethomics} framework are currently envisaged. 
They include utilities to input new behaviour tracking methods and analyse multi-animal interactions.

>>>>

\section*{Availability and Future Directions}
All packages in the \texttt{rethomics} framework are available under the terms of the GPLv3 license and are listed at
\href{https://rethomics.github.io/intro.html}{https://rethomics.github.io/intro.html}.
\texttt{behavr} and \texttt{damr} are already hosted on the Comprehensive R Archive Network (CRAN), and all the other packages are either under review or in preparation.
Extensive installation instructions, as well as reproducible demos and tutorials, are available at
\href{https://rethomics.github.io/}{https://rethomics.github.io/}.
All packages are continuously integrated and unit tested on several versions of \texttt{R} to minimise the risk of present and future issues.

Several users, in different research groups, have already adopted and are contributing to the future development of the framework.
Several new packages in the \texttt{rethomics} framework are currently envisaged. 
They include utilities to input new behaviour tracking methods and analyse multi-animal interactions.
